---
title: "BF Mosquito sampling"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
#get all of our stuff we need
pkg = c("rnaturalearthdata", "rnaturalearth", "tidyverse", "sf", "lubridate", "ggspatial", "raster")
#install.packages(pkg) #install packages if you need them and load
new.packages <- pkg[!(pkg %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
lapply(pkg, require, character.only = TRUE)#

setwd('~/OneDrive - University of Glasgow/MOVE/samples/')

#read sample data from 14 and 15 and bind together
bf_samples_14_15 = rbind(read.csv("MosquitoesDensity_2014_MV.csv"), 
                         read.csv("MosquitoesDensity_2015_MV.csv"))

#read bf cluster coords
bf_coords = read.csv("cluster_coords.csv")
bf_netdata = read.csv("NetsRollout_MV.csv")
bf_rollout = read.csv('rollout_mv.csv')

clustersamplecount = 10

s = bf_rollout %>% 
  dplyr::select(cluster, season) %>% 
  distinct() %>% 
  group_by(cluster) %>% 
  count() %>% 
  filter(n > 6) %>% 
  mutate(tag="tag")

bf_rollout_tagged = bf_rollout %>% 
  left_join(.,(s[sample(nrow(s), clustersamplecount), ])) #join to random sample of the tag df
  


#get africa maps sf
africa = ne_countries(scale="medium", type='countries', continent='africa', returnclass = "sf")
```
```{r plot, echo = F, fig.height = 8, fig.width = 6, fig.align = "center"}
#get africa maps sf
ggplot(data=africa)+
  geom_sf() +
  geom_point(data=bf_rollout_tagged, aes(x=lon, y=lat, colour=tag), size=1)+
  annotation_scale(location = "bl", width_hint = 0.5) +
  coord_sf(xlim= c(-5,-4), ylim = c(9.8,11))+
  facet_wrap(~season)
```

**Figure 1**: Rollout timeline broken down by season

```{r plot2, echo = F, fig.height = 8, fig.width = 6, fig.align = "center"}
#get africa maps sf
ggplot(data=africa)+
  geom_sf() +
  geom_point(data=bf_rollout_tagged, aes(x=lon, y=lat, colour=as.factor(rollout)), size=1)+
  annotation_scale(location = "bl", width_hint = 0.5) +
  coord_sf(xlim= c(-5,-4), ylim = c(9.8,11))+
  facet_wrap(~season)
```
**Figure 2**: Random sampling of 10 clusters consistently over time time period 
```{r calc, include=FALSE}
seasoncount = bf_rollout_tagged %>% dplyr::select(season) %>% distinct() %>% count()
samplesize = 10
num_samples = seasoncount*clustersamplecount*samplesize
```
```{r ecoregions, echo = FALSE}
colors = read.csv('rastermetadata.csv', header =F)
s = raster('~/Downloads/PROBAV_LC100_global_v3.0.1_2019-nrt_Discrete-Classification-map_EPSG-4326.tif') #load raster file
e = extent(-5, -4, 9.8, 11) #define extent to crop
bf = crop(s, e) #crop raster
bfdf = as.data.frame(rasterToPoints(bf))
colnames(bfdf) = c('x', 'y', 'cover')

colours = as.vector(colors$V2)
bfdf$cover = as.factor(bfdf$cover)

ggplot() +
  geom_raster(data = bfdf , aes(x = x, y = y, fill = cover)) +
  scale_fill_manual(values = colours) +
  geom_point(data=bf_rollout_tagged, aes(x=lon, y=lat), colour = '#ff0000', size=2)
```


**Figure 3**: Clusters plotted on a map of land cover. See the metadata table but briefly: 126 is forest, 40 is agriculture, 20 is shrubs, 50 is urban. 

The land cover data above is from [here](https://land.copernicus.eu/global/products/lc) from Copernicus.

I hate almost everything about this plot but generally it looks like a cline of thinning forest from S-N with some shrubland roughly where Mafalda defined the forest park as. So let's make sure we have some samples represented by all of these. 

```{r plottext, echo=FALSE, warning=FALSE}
ggplot() +
  geom_raster(data = bfdf , aes(x = x, y = y, fill = cover), alpha = 0.7) +
  scale_fill_manual(values = colours) +
  geom_text(data=bf_rollout_tagged, aes(x=lon, y=lat, label=cluster), colour = '#ff0000')
```

Toggling the opacity so the general horrendousness of the colour and annotations doesn't kill us. But I think let's pick: **37, 8, 27, 23, 32, 13, 12, 35, 24, 18, 10**

```{r plotpicks, echo= FALSE, warning=FALSE}
picks = as.data.frame(pick_clusters)
picks$newtag = "picked"
colnames(picks) = c('cluster', 'picktag')
bf_picks = left_join(bf_rollout_tagged, picks)
bf_picks$picktag=replace_na(bf_picks$picktag, 'notpicked')

ggplot() +
  geom_raster(data = bfdf , aes(x = x, y = y, fill = cover), alpha = 1) +
  scale_fill_manual(values = colours) +
  geom_point(data=bf_picks, aes(x=lon, y=lat, colour=picktag), size = 2, alpha = 1.5, colours = c('red', 'blue'))
```

**Fig 4** Picked/unpicked samples. Sorry about the colours.


**Table 1** Metadata table for land cover values
```{r ecotable, echo=FALSE}
colors
```